Dismal Code: Studying the Evolution of Security Bugs

### 2013-02-08 docs/msr.tex
more changes

\begin{itemize}
	\item The analysis of how security bugs evolve over time. To achieve
this, we inspect every project per version. Our hypothesis is that security
bugs must decrease as a project evolves since they are critical and developers
should eliminate them.
	\item We show evidence of the relation between security bugs and the artifact's size.  Here, size is
defined in terms of bytecode.
	\item Security bug persistense between versions. We show evidence that specific bugs are
not eliminated between versions.
	\item The correlation of security bugs with other bug categories. We
show evidence that such bugs are correlated with bugs that have to do with
performance, coding practices and others.
	\item The relation of software dependencies and security bugs. Our
hypothesis is that an artifact that is a dependency of many other artifacts
should have a low rate of security bugs. 
\end{itemize}

In the rest of this paper we
describe the processing of our data and our experiment (Section \ref{sec:meth}),
present and discuss the results we obtained (Section \ref{sec:res},
outline related work (Section \ref{sec:rel}),
and end up with an conclusion and directions for future work (Section \ref{sec:con}).

@@

\begin{figure*}
	\centering
	\includegraphics[scale=0.6]{version_count.pdf}
	\caption{Distribution of version count among project population}
	\label{fig:version-count}
\end{figure*}

@@

Figure~\ref{fig:bug-per} shows how software bugs are distributed among the
repository. Together with the {\it Bad Practice} bugs and the {\it Style} bugs,
security bugs (the sum of the {\it Security} and {\it Malicious Code}
categories) are the most popular in the repository. In the following section we
show the correlation of security bugs with all the other categories. An interesting observation is
that 5,601 (31.99\%) projects, containing 32,689 artifacts (28.57\%), did not
have any bugs at all. These cases involved small artifacts with a minimum number of classes.
This consorts with the relationship between the size of an artifact and it's
bugs that is presented in the upcoming section.

>>>>

\begin{itemize}
	\item The analysis of how security bugs evolve over time. To achieve
this, we inspect every project per version. Our hypothesis is that security
bugs must decrease as a project evolves since they are critical and developers
should eliminate them.
	\item We show evidence of the relation between security bugs and the artifact's size.  Here, size is
defined in terms of bytecode.
%	\item Security bug persistense between versions. We show evidence that specific bugs are
%not eliminated between versions.
	\item The correlation of security bugs with other bug categories. We
show evidence that such bugs are correlated with bugs that have to do with
performance, coding practices and others.
	\item The relation of software dependencies and security bugs. Our
hypothesis is that an artifact that is a dependency of many other artifacts
should have a low rate of security bugs. 
\end{itemize}

In the rest of this paper we
describe the processing of our data and our experiment (Section \ref{sec:meth}),
present and discuss the results we obtained (Section \ref{sec:res}),
outline related work (Section \ref{sec:rel}),
and end up with a conclusion and directions for future work (Section \ref{sec:con}).

@@

\begin{figure*}
	\centering
	\includegraphics[scale=0.6]{version_count.pdf}
	\caption{Distribution of
Version Count Among Project Population}
	\label{fig:version-count}
\end{figure*}

@@

Figure~\ref{fig:bug-per} shows how software bugs are distributed among the
repository. Together with the {\it Bad Practice} bugs and the {\it Style} bugs,
security bugs (the sum of the {\it Security} and {\it Malicious Code}
categories) are the most popular in the repository. This could be an indication
that programmers write code that implements the required functionality without considering
its many security aspects. In the following section we
show the correlation of security bugs with all the other categories. An interesting observation is
that 5,601 (31.99\%) projects, containing 32,689 artifacts (28.57\%), did not
have any bugs at all. These cases involved small artifacts with a minimum number of classes.
This goes along with the relationship between the size of an artifact and it's
bugs that is presented in the upcoming section.
